\section{Expected Results}

Upon completion of this research, we anticipate the following outcomes:

\subsection{Comprehensive Guide}

A detailed, user-friendly guide aimed at simplifying the process of implementing Trust Over Internet Protocols (ToIP). Tailored to various roles within the ToIP framework, this guide is expected to be instrumental in accelerating the integration and adoption of ToIP. By demystifying complex processes, it empowers users to harness the full potential of these systems.

\subsection{Development of Agents}
The creation of distinct agents for both the Issuer and the Verifier within the trust triangle. This development aims to provide a lucid understanding of their specific roles, offering users enhanced control and flexibility in tailoring ToIP protocols to their unique requirements.

\subsection{Wallet Integration}
The use of a wallet as a holder will streamline interactions with the Issuer and Verifier agents through interoperable objects. This is anticipated to simplify the overall creation process, thus enhancing the accessibility and intuitiveness of ToIP implementations.

\subsection{Interaction Mapping}
A thorough mapping of the extent and methodology of interactions between the trust triangle components. This deep dive is predicted to enrich our comprehension of the individual and collective roles in trust formation, paving the way for the development of more robust and effective ToIP protocols.

\subsection{Documentation}
A systematic documentation of the ToIP protocol implementation across the trust triangle. This roadmap aims to clarify the implementation process for users. By providing a clear, step-by-step guide, we expect to foster an environment where ToIP can be widely and confidently adopted, irrespective of a user's technical acumen.
