\subsection{Work Structure}

\subsubsection{Introduction}
\begin{enumerate}
    \item Brief about the importance of Trust Over Internet protocols in the digital age.
    \item The problem statement that led to this research.
\end{enumerate}

\subsubsection{State of the art}
\begin{enumerate}
    \item Comprehensive analysis of the present landscape, highlighting recent advancements.
    \item An overview of established best practices within the Trust Over Internet domain.
\end{enumerate}

\subsubsection{Methodology}
\begin{enumerate}
    \item Deep dive into existing literature to establish a foundation for the project.
    \item Details on creating distinct agents for the roles of Issuer and Verifier within the trust triangle.
    \item Steps and rationale behind using a wallet as the Holder.
    \item Explanation of how interactions between the trust triangle components are charted.
    \item Description of how findings from the above steps will be integrated into a comprehensive guide for Trust Over Internet protocols.
    \item A projection of the time required for each phase of the project.
\end{enumerate}

\subsubsection{Expected Results}
\begin{enumerate}
    \item A detailed forecast of the project's outcomes, spotlighting the creation of the comprehensive guide.
    \item The significance of distinct agents for the Issuer and Verifier in the trust triangle.
\end{enumerate}

\subsubsection{Discussion}
\begin{enumerate}
    \item Potential challenges in implementing the guide.
    \item Implications of the research and its findings for the wider industry.
\end{enumerate}

\subsubsection{Bibliography}
\begin{enumerate}
    \item A meticulously curated list of all references and sources consulted during the research.
\end{enumerate}
